Making Q-learning robust to time discretization

### 2019-01-16 paper/icml_drau/icml_drau.tex
add tmp title
Commiting

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Deep Relativistic Advantage Updating}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}

@@

\twocolumn[
\icmltitle{There are no small Advantages:
	Reinforcement learning in near continuous time
	with Deep RelAtive Mixture of Advantages
}

@@

\begin{abstract}
	Despite remarkable successes, \emph{Deep Reinforcement learning} (DRL) remains sensitive to
	hyperparameterization, implementation details and small environment changes~(\citealt{drl_matter}, \citealt{drl_matter_bis}). 
	Overcoming this sensitivity is key to making DRL applicable to real world problems.
	In this paper, we study the sensitivity of DRL to
	time discretization in \emph{near continuous time} environments. More precisely, we show that approaches based on estimations of the
	Q-function, e.g. \emph{Deep Q-learning}~\cite{dqn} and \emph{Deep deterministic policy gradient}~\cite{ddpg}
	are sensitive to variations of time discretization.
        We detail a principled method to obtain an off-policy RL algorithm that is more robust to changes in time discretization, and demontrate this robustness empirically. 
        % We further show that a simple reparameterization of the
	% Q-function as a sum of a state value term and a \emph{small} action dependent advantage term yields an algorithm
	% much more resilient to variations of time discretization.\LB{Change last sentence to: We introduce a more resilient algorithm to variations of time discretization [We could say more, but still less that what is already there]}
\end{abstract}

>>>>

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Making Q-learning robust to time discretization}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{result}{Result}

@@

\twocolumn[
\icmltitle{Making Q-learning robust to time discretization}

@@

\begin{abstract}
	Despite remarkable successes, \emph{Deep Reinforcement learning} (DRL) remains not robust to
	hyperparameterization, implementation details and small environment changes~(\citealt{drl_matter}, \citealt{drl_matter_bis}). 
	Overcoming this sensitivity is key to making DRL applicable to real world problems.
	In this paper, we study the sensitivity of DRL to
	time discretization in \emph{near continuous time} environments. More precisely, we show that approaches based on estimations of the
	Q-function, e.g. \emph{Deep Q-learning}~\cite{dqn} and \emph{Deep deterministic policy gradient}~\cite{ddpg}
	are sensitive to variations of time discretization.
        We detail a principled method to obtain an off-policy RL algorithm that is more robust to changes in time discretization, and demontrate this robustness empirically. 
        % We further show that a simple reparameterization of the
	% Q-function as a sum of a state value term and a \emph{small} action dependent advantage term yields an algorithm
	% much more resilient to variations of time discretization.\LB{Change last sentence to: We introduce a more resilient algorithm to variations of time discretization [We could say more, but still less that what is already there]}
\end{abstract}

### 2019-01-16 paper/icml_drau/intro.tex
Commiting

\section{Introduction}
\label{sec:intro}
In recent years, \emph{Deep Reinforcement Learning} (DRL) approaches have
thrived and provided impressive results in a variety of domains, achieving superhuman
performances with no expert knowledge in perfect information zero-sum
games~\cite{alphazero}, reaching level of top players in video
games~(\citealt{openai_five}, \citealt{dqn}), or learning dexterous manipulation
from scratch without demonstrations~\cite{hand_control}. 
In spite of those successes, DRL approaches are
sensitive to a number of factors, including hyperparameterization,
implementation details or small changes in the environment
parameters~(\citealt{drl_matter}, \citealt{drl_matter_bis}). This sensitivity,
along with sample inefficiency, prevents DRL from being applied in most real
world settings. High sensitivity to environment parameters notably prevents
transfering abilities from imperfect simulators to real world scenarios.

In this paper we focus our attention on the sensitivity to time discretization
of DRL approaches,
i.e. what happens when an agent receives $50$ observations
and is expected to take $50$ actions per second instead of $10$. One expects
that decreasing time discretization, or equivalently shortening reaction time,
should only improve agent performances. Robustness to time discretization is notably relevant in \emph{near-continuous}
environments, which includes most continuous control environments, robotics and many video games.
\TODO{Explain that it also includes $\gamma \rightarrow 1$.}

@@

A time discretization invariant algorithm should
in particular admit a time continuous limit i.\,e. when the discretization timestep goes to $0$.
This leads to precise design choices in term of
agent architecture, exploration policy and learning rates scalings.
The resulting algorithm is shown to provide near perfect invariance to time
discretization on simple environments, and much better invariance properties
than vanilla DQN or DDPG on more complex environments (Sec.~\ref{sec:exp}).
On a new environment, as soon as the order of magnitude of the time discretization is known, our analysis readily provides salient scalings for a number of hyperparameters.

Our contribution is threefold:
\begin{itemize} 
\item We formally show that the Q-function collapses to the V-function in near-continuous time, and thus that
    standard Q-learning is ill-behaved in this setting.
  \item Our analysis of limit properties in near continuous environments leads us to define a robust methods off-policy algorithm. In particular,
    it provides insights on how to design architectures, how to explore, and how to scale learning rates.
  \item We empirically show that standard Q-learning methods are not robust to changes in time discretization, and that our algorithm provides huge gain in that domain.
\end{itemize}

>>>>

\section{Introduction}
\label{sec:intro}
In recent years, \emph{Deep Reinforcement Learning} (DRL) approaches have
provided impressive results in a variety of domains, achieving superhuman
performance with no expert knowledge in perfect information zero-sum
games~\cite{alphazero}, reaching level of top players in video
games~(\citealt{openai_five}, \citealt{dqn}), or learning dexterous manipulation
from scratch without demonstrations~\cite{hand_control}. 
In spite of those successes, DRL approaches are
sensitive to a number of factors, including hyperparameterization,
implementation details or small changes in the environment
parameters~(\citealt{drl_matter}, \citealt{drl_matter_bis}). This sensitivity,
along with sample inefficiency, prevents DRL from being applied in real
world settings. High sensitivity to environment parameters notably prevents
transfer of abilities from imperfect simulators to real world scenarios.

In this paper we focus our attention on the sensitivity to time discretization
of DRL approaches,
i.e. what happens when an agent receives $50$ observations
and is expected to take $50$ actions per second instead of $10$. One expects
that decreasing time discretization, or equivalently shortening reaction time,
should only improve agent performance. Robustness to time discretization is notably relevant in \emph{near-continuous}
environments, which includes most continuous control environments, robotics and many video games.
More generally, robusteness to time discretization is important in any setting in which the advantage
an individual action over another is small compared to the total return, and notably on long time horizon
problems.

@@

A time discretization invariant algorithm should in particular admit a time
continuous limit i.\,e. when the discretization timestep goes to $0$.  This
leads to precise design choices in term of agent architecture, exploration
policy and learning rates scalings.  The resulting algorithm is shown to
provide better invariance to time discretization on many environments than
vanilla DQN or DDPG (Sec.~\ref{sec:exp}).  On a new environment, as soon as the
order of magnitude of the time discretization is known, our analysis readily
provides relevant scalings for a number of hyperparameters.

Our contribution is threefold:
\begin{itemize} 
\item We show that the Q-function collapses to the V-function in near-continuous time, and thus that
    standard Q-learning is ill-behaved in this setting.
  \item Our analysis of limit properties in near continuous environments leads to a robust off-policy algorithm. In particular,
    it provides insights on how to design architectures, constraints exploration, as well as learning rates scalings.
  \item We empirically show that standard Q-learning methods are not robust to changes in time discretization, and that our algorithm provides huge gain in that domain.
\end{itemize}
